\section{Supplementary Reproducibility Record}

\paragraph{Data and evaluator.}
All methods consume the frozen \texttt{paper\_raw\_v1} row contract.
The corrected evaluator covers 80,651 Steam, 85,405 ML1M, 2,237 Beauty,
and 1,942 ATG test rows. The dated E0 amendment retains legacy values
and applies the corrected ruler to every method rather than replacing
selected cells.

\paragraph{Evidence layers.}
$U_{ds}$ is a train-only discovery statistic computed from 4,000
training transitions and 100 popularity negatives per transition. EPE
is the observed next-positive exposure proxy
$\log(q_{\rm text}(y\mid h)+10^{-12})-
\log(q_{\rm core}(y)+10^{-12})$. The atomic pilot freezes
$\phi_R=1.0/0.136631/0.0$ for Beauty and
$1.0/0.058081/0.0$ for Steam under c0/c60/c100. These quantities have
different evidential roles.

\paragraph{Implementation trace.}
The historical E1 step-0 mismatch was preserved. After repair, the
designated R12 trace at revision \texttt{0338cc2} performed 2,986
comparisons with zero failures. This trace is scoped to its designated
Beauty path and does not certify every dataset, checkpoint, or auxiliary
injection mode.

\paragraph{External baseline.}
The adapted SASRec implementation reads the frozen frames, changes only
padding orientation, uses full-softmax training and full-real-catalog
evaluation, and selects by validation NDCG@10. It is a common-contract
baseline rather than an official-protocol reproduction. All four
domains are reported atomically, including Beauty's validation-to-test
decline.

\paragraph{Uncertainty and test use.}
All new training reported in this cycle uses seed 100 and is described
as a single-run observation. Frozen transition records lack user IDs,
so E7 ran zero bootstrap replicates and user-level uncertainty is not
estimable. Model selection used validation only; test metrics were
logged during development, so test is not described as an untouched
final holdout.

\paragraph{Artifact release.}
The local evidence package inventories 70 immutable inputs by SHA-256.
Atomic r7 performance is released only after 14/14 active tasks,
nonempty task and training logs, valid artifact manifests, consistent
RISK-08/TERMINAL markers, and a \texttt{risk\_gated\_method} exit.
